\begin{abstract} \label{astract}
FrodoKEM is a lattice-based key encapsulation mechanism, currently a semi-finalist in NIST's post-quantum standardization effort. A condition for these candidates is to use NIST standards for PRNG / seed-expanding, and as such most candidates utilize SHAKE, an XOF defined in the SHA-3 standard. However, for many of the candidates, this module is a significant implementation bottleneck. Trivium is a lightweight, ISO standard stream cipher which performs well in hardware and has been used in previous hardware designs for lattice-based cryptography. This research proposes optimized designs for FrodoKEM, concentrating on high throughput by parallelising the matrix multiplication operations within the cryptographic scheme. This process is eased by the use of Trivium due to its higher throughput and lower area consumption. The parallelisations proposed also complement the addition of first-order masking to the decapsulation module. Overall, we significantly increase the throughput of FrodoKEM; for encapsulation we see a 16x speed-up and for decapsulation we see a 14x speed-up compared to the previous state-of-the-art, whilst also maintaining a similar FPGA area footprint.

%achieving up to 840 key generations per second, 825 encapsulations per second, and 763 decapsulations per second, with almost no impact on the FPGA area consumption compared to the previous state-of-the-art.


%Recently, a standard lattice-based key encapsulation mechanism has been shown to have promising performance on FPGA. The cryptographic scheme, named FrodoKEM, is one of many candidates for NIST's call for post-quantum standardisation. This research proposes optimised designs for FrodoKEM, concentrating on high throughput by parallelising the matrix multiplication operations within the cryptographic scheme. This process is eased by the use of a much smaller and faster PRNG. The parallelisations proposed also complement the addition of first-order masking to the decapsulation module. Overall, we significantly increase the throughput of FrodoKEM, achieving up to 840 key generations per second, 825 encapsulations per second, and 763 decapsulations per second, with almost no impact on the FPGA area consumption compared to the previous state-of-the-art.

\end{abstract}

%\begin{IEEEkeywords}
%post-quantum cryptography, lattice-based cryptography, FPGA, hardware security, masking
%\end{IEEEkeywords}